Decentralized Data Marketplace to Enable Trusted Machine Economy

### 2019-08-10 paper.tex
Apply to IEEE latex template

\documentclass{svproc}

% to typeset URLs, URIs, and DOIs
\usepackage{url}
\def\UrlFont{\rmfamily}

\begin{document}
\mainmatter              % start of a contribution
%
\title{Data Marketplace for Streaming Data}
%
\titlerunning{Streaming Data Marketplace}  % abbreviated title (for running head)
%
\author{Ching-Chun Huang \and Ching-Hua Lin
}
%
\authorrunning{Ching-Chun Huang et al.} % abbreviated author list (for running head)
\tocauthor{Ching-Chun Huang, Ching-Hua Lin}
%
\institute{National Cheng Kung University, Taiwan\\
\email{jserv.tw@gmail.com, jkrvivian@gmail.com}
}

\maketitle              % typeset the title of the contribution

%at least 70 words, at most 150 words
%It will be set in 9-point font size and be inset 1.0 cm from the right and left margins.
\begin{abstract}
abstract here
\keywords{streaming data, crowd sensing, data marketplace}
\end{abstract}

@@

% ---- Bibliography ----
\begin{thebibliography}{3}
%
\bibitem {DIaas}
Bin Liu, Xiao Liang Yu, Shiping Chen, Xiwei Xu and Liming Zhu. 
Blockchain based Data Integrity Service Framework for IoT data. In IEEE 24th International Conference on Web Services 2017.

\bibitem {IOTAwhitepaper}
S. Popov. Iota whitepaper. Technical White Paper. 2017

\bibitem {MAM}
Paul Handy. Masked Authenticated Messaging. Medium. 2017
\url https://blog.iota.org/introducing-masked-authenticated-messaging-e55c1822d50e

\end{thebibliography}
\end{document}

>>>>

\documentclass[journal,a4paper]{IEEEtran}

% to typeset URLs, URIs, and DOIs
\usepackage[english]{babel}
\usepackage{url}
\usepackage{multicol}
\usepackage{multirow}
\usepackage{url,hyperref,graphicx,float,times}
\usepackage{textcomp}
\usepackage{cite}
\usepackage[caption=false,font=footnotesize]{subfig}

\begin{document}
%
\title{Decentralized Data Marketplace to Enable Trusted Machine Economy}
%
\author{
%%% Fill in name here
\IEEEauthorblockN{Ching-Chun (Jim) Huang\IEEEauthorrefmark{1}, Ching-Hua Lin\IEEEauthorrefmark{2}} \\

%%% Fill in school here
\IEEEauthorblockA{\IEEEauthorrefmark{1}\IEEEauthorrefmark{2}Department of Computer Science and Information Engineering National Cheng Kung University} \\

%%% Fill in address here
\IEEEauthorblockA{\IEEEauthorrefmark{1}\IEEEauthorrefmark{2}No.1, University Road} \\

%%% Fill in city and country here
\IEEEauthorblockA{\IEEEauthorrefmark{1}\IEEEauthorrefmark{2}Tainan City, Taiwan (R.O.C.)} \\

%%% Fill in email here
\IEEEauthorblockA{\IEEEauthorrefmark{1}jserv.tw@gmail.com, \IEEEauthorrefmark{2}jkrvivian@gmail.com}
}

%

\maketitle              
% 50-80 words
\begin{abstract}
abstract here
\end{abstract}

% 3 - 4 keywords
\begin{IEEEkeywords}
streaming data, crowd sensing, data marketplace, decentralization
\end{IEEEkeywords}

@@

\section{System Architecture}

\section{Trading Model}

\section{Conclusion}

% ---- Bibliography ----
\bibliographystyle{IEEEtran}
\bibliography{references}

\end{document}
